\begin{thebibliography}{}

 \bibitem{prag_prog:dupl}
  \emph{The Pragmatic Programmer.}
  Hunt A., Thomas D.
  Addison-Wesley.
  Westford 2013.
  ISBN 0-201-61622-X.
  \emph{The Evils of Duplication}, s. 26-33.
 
 \bibitem{prag_prog:entropy}
  \emph{The Pragmatic Programmer.}
  Hunt A., Thomas D.
  Addison-Wesley.
  Westford 2013.
  ISBN 0-201-61622-X.
  \emph{Software Entropy}, s. 4-6.
 
 \bibitem{soft_sol_dupl}
  \emph{Duplication in Software} [online].
  Just Software Solutions.
  http://www.justsoftwaresolutions.co.uk/design/duplication.html [dostęp: lipiec 2014].
  
 \bibitem{repetition}
  \emph{Repetition} [online].
  The Bad Code Spotter's Guide.
  Diomidis Spinellis.
  http://www.informit.com/articles/article.aspx?p=457502\&seqNum=5 [dostęp: lipiec 2014].
 
 \bibitem{cont_delivery}
  \emph{Continous delivery} [online].
  ThoughtWorks.
  http://www.thoughtworks.com/continuous-delivery [dostęp: lipiec 2014].
 
 \bibitem{entity_framework}
  \emph{Enity Framework} [online].
  CodePlex.
  https://entityframework.codeplex.com/ [dostęp: lipiec 2014].
 
 \bibitem{sqlmetal}
  \emph{SqlMetal.exe (Code Generation Tool)} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/pl-pl/library/bb386987(v=vs.110).aspx [dostęp: lipiec 2014].
 
 \bibitem{django}
  \emph{The Web framework for perfectionists with deadlines} [online].
  django.
  https://www.djangoproject.com/ [dostęp: lipiec 2014].
  
 \bibitem{hibernate}
  \emph{Hibernate. Everything data.} [online].
  Hibernate.
  http://http://hibernate.org/ [dostęp: lipiec 2014].
  
 \bibitem{doxygen}
  \emph{Doxygen: Main Page} [online].
  Doxygen.
  http://www.stack.nl/~dimitri/doxygen/ [dostęp: lipiec 2014].
  
 \bibitem{javadoc}
  \emph{Javadoc Tool Homepage} [online].
  Oracle.
  http://www.oracle.com/technetwork/java/javase/documentation/index-jsp-135444.html [dostęp: lipiec 2014].
  
 \bibitem{msdn:xml_doc}
  \emph{XML Documentation} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/b2s063f7(vs.71).aspx [dostęp: lipiec 2014].
  
 \bibitem{pydoc}
  \emph{pydoc — Documentation generator and online help system} [online].
  Python v2.7.8 documentation.
  https://docs.python.org/2/library/pydoc.html [dostęp: lipiec 2014].
 
 \bibitem{auto_prog}
  \emph{Automatic programming} [online].
  Wikipedia, the free encyclopedia.
  http://en.wikipedia.org/wiki/Automatic\_programming [dostęp: lipiec 2014].
 
 \bibitem{xslt}
  \emph{XSL Transformations (XSLT) Version 2.0} [online].
  W3C.
  http://www.w3.org/TR/xslt20/ [dostęp: lipiec 2014].
 
 \bibitem{uml}
  \emph{Unified Modeling Language\texttrademark (UML\textregistered)} [online].
  Object Management Group.
  http://www.uml.org/ [dostęp: lipiec 2014].
 
 \bibitem{xml}
  \emph{Extensible Markup Language (XML)} [online].
  W3C.
  http://www.w3.org/XML/ [dostęp: lipiec 2014].
 
 \bibitem{wsdl}
  \emph{Web Services Description Language (WSDL) 1.1} [online].
  W3C.
  http://www.w3.org/TR/wsdl [dostęp: lipiec 2014].
  
 \bibitem{json}
  \emph{Introducing JSON} [online].
  Ecma International.
  http://json.org/ [dostęp: lipiec 2014].
 
 \bibitem{odata}
  \emph{Open Data Protocol} [online].
  OData.
  http://www.odata.org/ [dostęp: lipiec 2014].
 
 \bibitem{yaml}
  \emph{The Official YAML Web Site} [online].
  Evans C.
  http://www.yaml.org/ [dostęp: lipiec 2014].
 
 \bibitem{w3c}
  \emph{World Wide Web Consortium (W3C)} [online].
  W3C.
  http://www.w3.org/ [dostęp: lipiec 2014].
 
 \bibitem{razor}
  \emph{RazorEngine} [online].
  GitHub.
  https://github.com/Antaris/RazorEngine [dostęp: lipiec 2014].

 \bibitem{t4}
  \emph{Code Generation and T4 Text Templates} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/pl-pl/library/bb126445.aspx [dostęp: lipiec 2014].
 
 \bibitem{ntier}
  \emph{N-Tier Data Applications Overview} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/bb384398.aspx [dostęp: lipiec 2014].
 
 \bibitem{three_tier}
  \emph{Three tier architecture in asp.net} [online].
  Dot Net Peoples.
  http://dotnetpeoples.blogspot.com/2011/04/three-tier-architecture-in-aspnet.html [dostęp: lipiec 2014].

 \bibitem{business_object}
  \emph{Business object} [online].
  Wikipedia, the free encyclopedia.
  http://en.wikipedia.org/wiki/Business\_object [dostęp: lipiec 2014].
  
 \bibitem{view_model}
  \emph{View model} [online].
  Wikipedia, the free encyclopedia.
  http://en.wikipedia.org/wiki/View\_model [dostęp: lipiec 2014].
 
 \bibitem{dto}
  \emph{Data Transfer Object} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/ms978717.aspx [dostęp: lipiec 2014].
 
 \bibitem{cqrs_journey}
  \emph{Exploring CQRS and Event Sourcing}
  Betts D., Domínguez J., Melnik G., Simonazzi F., Subramanian M.
  Microsoft.
  2012.
  ISBN 978-1-62114-016-0.
 
 \bibitem{cqrs_fowler}
  \emph{CQRS} [online].
  Fowler M.
  http://martinfowler.com/bliki/CQRS.html [dostęp: lipiec 2014].
 
 \bibitem{eventSourcing_msdn}
  \emph{Event Sourcing Pattern} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/dn589792.aspx [dostęp: lipiec 2014].
 
 \bibitem{eventSourcing_intro}
  \emph{Introducing Event Sourcing} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/jj591559.aspx [dostęp: lipiec 2014].
 
 \bibitem{youtube}
  \emph{YouTube} [online].
  YouTube.
  https://www.youtube.com/ [dostęp: lipiec 2014].
 
 \bibitem{youtube:301}
  \emph{Why do YouTube views freeze at 301?} [online].
  Numberphile.
  YouTube.
  https://www.youtube.com/watch?v=oIkhgagvrjI [dostęp: lipiec 2014].
 
 \bibitem{cqrs_es}
  \emph{CQRS and Event Sourcing} [online].
  Wordpress.
  http://cqrs.wordpress.com/documents/cqrs-and-event-sourcing-synergy/ [dostęp: lipiec 2014].
  
 \bibitem{cqrs_info}
  \emph{CQRS Info} [online].
  CQRS Info.
  http://www.cqrsinfo.com/ [dostęp: lipiec 2014].

 \bibitem{hadoop}
  \emph{Welcome to Apache\texttrademark Hadoop\textregistered!} [online].
  The Apache Software Foundation.
  http://hadoop.apache.org/ [dostęp: lipiec 2014].
 
 \bibitem{cassandra}
  \emph{The Apache Cassandra Project} [online].
  The Apache Software Foundation.
  https://cassandra.apache.org/ [dostęp: lipiec 2014].
 
 \bibitem{simple_db}
  \emph{Amazon SimpleDB} [online].
  Amazon Web Services.
  http://aws.amazon.com/simpledb/ [dostęp: lipiec 2014].
 
 \bibitem{mongo_db}
  \emph{MongoDB} [online].
  MongoDB.
  http://www.mongodb.org/ [dostęp: lipiec 2014].
 
 \bibitem{couch_db}
  \emph{Apache CouchDB} [online].
  The Apache Software Foundation.
  http://couchdb.apache.org/ [dostęp: lipiec 2014].
 
 \bibitem{raven_db}
  \emph{Raven DB} [online].
  GitHub.
  https://github.com/ravendb/ravendb [dostęp: lipiec 2014].
 
 \bibitem{dynamo_db}
  \emph{Amazon DynamoDB} [online].
  Amazon Web Services.
  http://aws.amazon.com/dynamodb/ [dostęp: lipiec 2014].
 
 \bibitem{azure_table_storage}
  \emph{Table Service REST API} [online].
  Microsoft Developer Network.
  http://msdn.microsoft.com/en-us/library/dd179423.aspx [dostęp: lipiec 2014].
 
 \bibitem{redis}
  \emph{Redis} [online].
  Citrusbyte.
  http://redis.io/ [dostęp: lipiec 2014].
 
 \bibitem{neo4j}
  \emph{Neo4j - The World's Leading Graph Database} [online].
  Neo Technology.
  http://www.neo4j.org/ [dostęp: lipiec 2014].
 
 \bibitem{titan}
  \emph{Titan} [online].
  GitHub.
  https://github.com/thinkaurelius/titan/wiki [dostęp: lipiec 2014].
 
 \bibitem{trinity}
  \emph{Trinity - Microsoft Research} [online].
  Microsoft Research.
  http://research.microsoft.com/en-us/projects/trinity/ [dostęp: lipiec 2014].
 
 \bibitem{cassandra_perf}
  \emph{Solving Big Data Challenges for Enterprise Application Performance Management} [online].
  Rabl T., Sadoghi M., Jacobsen H.
  http://vldb.org/pvldb/vol5/p1724\_tilmannrabl\_vldb2012.pdf [dostęp: lipiec 2014].
 
 \bibitem{cassandra_architecture}
  \emph{Multiple data center write requests} [online].
  DataStax Cassandra 1.2 Documentation.
  http://www.datastax.com/documentation/cassandra/1.2/cassandra/architecture/architectureClientRequestsMultiDCWrites\_c.html [dostęp: sierpień 2014].
 
 \bibitem{cassandra_model}
  \emph{Cassandra Data Modeling Best Practices, Part 1} [online].
  Patel J.
  eBay tech blog.
  http://www.ebaytechblog.com/2012/07/16/cassandra-data-modeling-best-practices-part-1/ [dostęp: lipiec 2014].
 
 \bibitem{cassandra:collections}
  \emph{Using collections} [online].
  DataStax CQL 3.0 Documentation.
  http://www.datastax.com/documentation/cql/3.0/cql/cql\_using/use\_collections\_c.html [dostęp: lipiec 2014].
  
\end{thebibliography}
